HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-18 paper/main.tex
minor corrections

In order to validate the HUME metric, we ran an annotation experiment with one source language (English),
and four target languages (Czech, German, Polish and Romanian), using text from the public health domain.
The domain is particularly suitable for experimenting on MT evaluation, as semantically
accurate translation is paramount here, underscoring the importance of accurate
semantic evaluation measures.

@@

For each of the four language pairs under consideration  we built phrase-based MT systems
using Moses \parcite{Koehn:2007}. We used large training sets extracted from
OPUS \parcite{tiedemann:2009}, and
the data sets released for the WMT14 medical translation task \parcite{bojar-EtAl:2014:W14-33}, to provide between
45 and 85 million sentences of training data, depending on language pair.
%\oa{I think we should probably
%  say how many in each.}.
% ... if someone asks us to do so...

@@

Source sentences are all in English, and their UCCA annotation was performed by four
computational linguists and one linguist.

>>>>

In order to validate the HUME metric, we ran an annotation experiment with one source language (English),
and four target languages (Czech, German, Polish and Romanian), using text from the public health domain.
The domain is particularly suitable for experimenting on MT evaluation, as semantically
accurate translation is paramount here, underscoring the importance of reliable
semantic evaluation measures.

@@

For each of the four language pairs under consideration  we built phrase-based MT systems
using Moses \parcite{Koehn:2007}.  These were trained on large parallel data sets extracted from
OPUS \parcite{tiedemann:2009}, and
the data sets released for the WMT14 medical translation task \parcite{bojar-EtAl:2014:W14-33}, 
giving between 
45 and 85 million sentences of training data, depending on language pair.
%\oa{I think we should probably
%  say how many in each.}.
% ... if someone asks us to do so...

@@

The source sentences are all in English, and their UCCA annotation was performed by four
computational linguists and one linguist.
